\pkg{cv}: An \proglang{R} Package for Cross-Validating Regression Models

### 2024-07-14 scratch/notes_john/JSS-article/JSS-article-4.Rmd
change ` ` to \code{ } markup in JSS-article-4

The data for the example in this section are drawn from the \pkg{ISLR2} package for \proglang{R}, associated with @JamesEtAl:2021. The presentation here is close (though not identical) to that in the original source [@JamesEtAl:2021 Secs. 5.1, 5.3], and it demonstrates the use of the `cv()` function.[^boot]

[^boot]: @JamesEtAl:2021 use the `cv.glm()` function in the \pkg{boot} package [@CantyRipley2022; @DavisonHinkley:1997]. Despite its name, `cv.glm()` is an independent function and not a method of a `cv()` generic function. The \pkg{boot} package is part of the standard \proglang{R} distribution.

@@

```{r Auto}
data("Auto", package = "ISLR2")
summary(Auto)
```
With the exception of `origin` (which we don't use here), these variables are largely self-explanatory, except possibly for units of measurement: for details see `help("Auto", package="ISLR2")`.

@@

We'll focus on the relationship of \code{mpg} (miles per gallon) to \code{horsepower}, as displayed in Figure \ref{fig:mpg-horsepower-polynomials} (a). The relationship between the two variables is monotone, decreasing, and nonlinear. Following @JamesEtAl:2021, we'll consider approximating the relationship by a polynomial regression, with the degree of the polynomial $p$ ranging from 1 (a linear regression) to 10.[^log-trans] Polynomial fits  for $p = 1$ to $5$ are shown in Figure \ref{fig:mpg-horsepower-polynomials} (a). The linear fit is clearly inappropriate; the fits for $p = 2$ (quadratic) through $4$ are very similar; and the fit for $p = 5$ may over-fit the data by chasing one or two relatively high `mpg` values at the right (but see the CV results reported below).

[^log-trans]: Although it serves to illustrate the use of CV, a polynomial is not the best choice here. Consider, for example the scatterplot for log-transformed `mpg` and `horsepower`, produced by `plot(mpg ~ horsepower, data=Auto, log="xy")` (execution of which is left to the reader). We revisit the \code{Auto} data in Section \ref{cross-validating-model-specification}.

@@

The generic `cv()` function has an `"lm"` method,
```{r cv-lm-method}
args(cv:::cv.lm)
```
which takes the following arguments:

@@

```{r cv.lm-2`}
cv(m.auto, k = "loo")
```
The \code{"hatvalues"} method reports only the CV estimate of MSE. Alternative methods are to use the Woodbury matrix identity or the "naive" approach of literally refitting the model with each case omitted. All three methods produce exact results for a linear model (within the precision of floating-point computations); for example:
```{r cv.lm-3}
cv(m.auto, k = "loo", method = "naive", confint = TRUE)
```
The \code{"naive"} and \code{"Woodbury"} methods also return the bias-adjusted estimate of MSE (and a confidence interval around it) along with the full-sample MSE, but bias isn't an issue for LOO CV.

@@

[^code-in-complements]: The code for this section is in the complementary materials for the paper. We used the `glmmTMB()` function in the \pkg{glmmTMB} package [@BrooksEtAl] for the models fit here because, in our experience, it is more likely to converge than functions in the \pkg{nlme} and the \pkg{lme4} packages for models with low between-cluster variance. We used the \pkg{lattice} [@Sarkar:2008] and \pkg{latticeExtra} [@SarkarAndrews:2022] packages for the graphs.

@@

```{r plot1, echo=FALSE, cache=TRUE}
#| out.width = "75%",
#| fig.height = 2.5,
#| fig.cap = "Data sets showing identical within-patient configurations with increasing between-patient variance. The labels above each panel show the ratio of between-patient SD to within-patient SD. The ellipses are estimated 50% Gaussian concentration ellipses for each patient. The population between-patient regression line, $E(y) = 10 + x$, is shown in each panel, where $y$ is symptoms and $x$ is dosage."
library("lattice")
library("latticeExtra")
layer <- latticeExtra::layer # to avert conflicts with ggplot2::layer
xyplot(y ~ x | SD_ratio, data = Data, group = patient,
       ylab = list('symptoms (y)', cex = 0.7),
       xlab = list('dosage (x)', cex = 0.7),
       par.strip.text = list(cex = 0.7),
       scales = list(cex = 0.7, x = list(alternating = FALSE)),
       layout = c(Nv, 1),
       par.settings = list(superpose.symbol = list(pch = 1, cex = 0.7))) +
  layer(panel.ellipse(..., center.pch = 16, center.cex = 0.5,  
                      level = 0.5),
        panel.abline(a = 10, b = 1))
```

Using data like these, a researcher may attempt to obtain an estimate of the within-patient effect of dosage by fitting mixed models with a random intercept. We will illustrate how this approach results in estimates that are highly sensitive to the relative variance at the two levels of the mixed model by considering four models, all of which include a random intercept.  The first three models are sequentially nested in their fixed effects: (1) `~ 1`, intercept only; (2) `~ 1 + x`, intercept and effect of `x`; and (3) `~ 1 + x + xm`, intercept, effect of `x`, and a contextual variable, `xm`, consisting of the within-patient mean of `x`. The final model, (4) `~ 1 + I(x - xm)`, uses an intercept and the centered-within-group variable `x - xm`. We thus fit four models to four data sets for a total of 16 models.

@@

Data sets with relatively low between-patient variance result in strong shrinkage of fixed-effects predictions, and also of BLUPs, towards the between-patient relationship between `y` and `x` in the model with an intercept and `x` as fixed-effect predictors, `~ 1 + x`. The inclusion of the contextual variable `xm` in the model corrects this problem.

Although the BLUPs fit the observed data more closely than predictions based on fixed effects alone, the slopes of within-patient BLUPs do not conform to the within-patient slopes for the `~ 1 + x` model in the two data sets with the smallest between-patient variances. For data with a small between-patient variance, fixed-effects predictions for the `~ 1 + x` model have a slope that is close to the between-patient slope but provide better overall predictions than the fixed-effect predictions for data sets with larger between-subject variance.  With data whose between-patient variance is relatively large, predictions based on the model with a common intercept and slope for all clusters are very poor---indeed, much worse than the fixed-effects-only predictions based on the simpler random-intercept model.

We therefore anticipate (and show later in this section) that case-based cross-validation may prefer the intercept-only model, `~ 1`  to the larger `~ 1 + x` model when the between-cluster variance is relatively small, but that cluster-based cross-validation will prefer the latter to the former. We will discover that case-based cross-validation prefers the `~ 1 + x` model to the `~ 1` model for the '5 / 2.5' data set, but cluster-based cross-validation prefers the latter model to the former. The situation is entirely reversed with the '8 / 2.5' data set.

The third model, `~ 1 + x + xm`, includes a contextual effect of `x`---that is, the cluster mean `xm`---along with `x` and the intercept in the fixed-effect part of the model, and with a random intercept. This model is equivalent to fitting `y ~ I(x - xm) + xm + (1 | patient)`, which is the model that generated the data.  The fit of the mixed model `~ 1 + x + xm` is consequently similar to that of a fixed-effects-only model with `x` and a categorical predictor for individual patients (i.e., `y ~ factor(patient) + x`, treating patients as a factor, and not shown here).

@@

[^cv-list]: In order to reduce between-model random variability in comparisons of models on the same data set, we applied `cv()` to a list of models created by the `models()` function (introduced previously), performing cross-validation with the same folds for each model.

@@

```{r cross-validation-data,include=FALSE,cache=TRUE}
names(cvs_clusters) <- names(cvs_cases) <- SD_ratio 
dsummary <- expand.grid(SD_ratio_i = names(cvs_cases), model = names(cvs_cases[[1]]))
dsummary$cases <-
  sapply(1:nrow(dsummary), function(i){
    with(dsummary[i,], cvs_cases[[SD_ratio_i]][[model]][['CV crit']])
  })
dsummary$clusters <-
  sapply(1:nrow(dsummary), function(i){
    with(dsummary[i,], cvs_clusters[[SD_ratio_i]][[model]][['CV crit']])
  })
```
```{r cross-validation-data-plot,echo=FALSE}
#| out.width = "75%",
#| fig.height = 3,
#| fig.cap = "10-fold cluster- and case-based cross-validation comparing mixed models with random intercepts and various fixed effects."
xyplot(clusters + cases ~ model|SD_ratio_i, dsummary,
       auto.key = list(space = 'top', columns = 2, cex = 0.7), 
       type = 'b', ylab = list('CV criterion (MSE)', cex = .7),
       xlab = '',
       par.strip.text = list(cex = 0.7),
       layout= c(Nv, 1),
       par.settings =
         list(superpose.line=list(lty = c(1, 2), lwd = 1),
              superpose.symbol=list(cex = 0.7)),
       scales = list(y = list(log = TRUE, cex = 0.7), 
                     x = list(alternating = F, rot = 45, cex = 0.7))) 
```
In summary, when between-cluster variance is relatively large, the model `~ 1 + x`, with `x` alone and without the contextual mean `xm` of `x`, is assessed as fitting very poorly by cluster-based CV, but relatively much better by case-based CV. In all of our examples, the model `~ 1 + x + xm`, which includes both `x` and its contextual mean, produces better results using both cluster-based and case-based CV.  These conclusions are consistent with our observations based on graphing predictions from the various models, and they illustrate the desirability of assessing mixed-effect models at different hierarchical levels.

@@

After transforming both the numeric predictors and the response, we proceed to use the \code{stepAIC()} function in the \pkg{MASS} package to perform predictor selection, employing the BIC model-selection criterion (by setting the `k` argument of `stepAIC()` to $\log n$):
```{r stepAIC}
library("MASS")
m.step <- stepAIC(m, k = log(nrow(A)), trace = FALSE)
brief(m.step)
```

@@

In Section \ref{comparing-competing-models}, following @JamesEtAl:2021[Secs. 5.1, 5.3], we fit polynomial regressions up to degree 10 to the relationship of `mpg` to `horsepower` for the `Auto` data, saving the 10 models, named `m.1` through `m.10`, in the list `mlist`. We then used `cv()` to compare the cross-validated MSE for the 10 models, discovering that the 7th degree polynomial had the smallest MSE (by a small margin).

If we select the 7th degree polynomial model, intending to use it for prediction, the CV estimate of the MSE for this model will be optimistic. One solution is to cross-validate the process of using CV to select the "best" model---that is, to apply CV to CV recursively. The function `selectModelList()`, which is suitable for use with `cv()`, implements this idea.

Applying `selectModelList()` to the `Auto` polynomial-regression models, and using 10-fold CV, we obtain:
```{r recursive-CV-polynomials}
recursiveCV.auto <- cv(selectModelList, data = Auto, 
                       working.model = mlist, save.model = TRUE, 
                       seed = 2120)
recursiveCV.auto
brief(recursiveCV.auto$selected.model)
cv(mlist[[7]], seed = 2120)
```
As expected, recursive CV produces a larger estimate of MSE for the selected 7th degree polynomial model than CV applied directly to this model (using the same seed for \proglang{R}'s random-number generator to obtain the same folds).

We can equivalently call `cv()` with the list of models as its first argument and set the argument `recursive=TRUE` (identical output not shown):
```{r recursive-cv-alt, eval=FALSE}
cv(mlist, data = Auto, seed = 2120, recursive = TRUE, save.model = TRUE)
```

@@

head(GetResponse(m.beps))
```
and to try again:
```{r BEPS-test-default-2, error=TRUE}
cv(m.beps, seed = 3465, criterion = BayesRuleMulti)
```
A \code{traceback()} (not shown) reveals that the problem is that the default method of \code{cv()} calls the \code{"multinom"} method for \code{predict()} with the argument \code{type="response"}, when the correct argument should be \code{type="class"}.  We therefore must write a \code{"multinom"} method for \code{cv()}, but that proves to be very simple:
```{r cv.nultinom}
cv.multinom <- function (model, data, criterion = BayesRuleMulti, 
                         k, reps, seed, ...) {
    model <- update(model, trace = FALSE)
    NextMethod(
      type = "class", criterion = criterion,
      criterion.name = deparse(substitute(criterion))
    )
  }
```
That is, we simply call the default `cv()` method (via \code{NextMethod()}) with the `type` argument properly set. In addition to supplying the correct `type` argument, our method sets the default `criterion` for the `cv.multinom()` method to `BayesRuleMulti`. Adding the argument `criterion.name=` `deparse(substitute(criterion))` is inessential, but it insures that printed output will include the name of the criterion function that's employed, whether it's the default `BayesRuleMulti` or something else. Prior to invoking `NextMethod()`, we called `update()` with `trace=FALSE` to suppress the iteration history reported by default by `multinom()`---it would be tedious to see the iteration history for each fold.

>>>>

The data for the example in this section are drawn from the \pkg{ISLR2} package for \proglang{R}, associated with @JamesEtAl:2021. The presentation here is close (though not identical) to that in the original source [@JamesEtAl:2021 Secs. 5.1, 5.3], and it demonstrates the use of the \code{cv()} function.[^boot]

[^boot]: @JamesEtAl:2021 use the \code{cv.glm()} function in the \pkg{boot} package [@CantyRipley2022; @DavisonHinkley:1997]. Despite its name, \code{cv.glm()} is an independent function and not a method of a \code{cv()} generic function. The \pkg{boot} package is part of the standard \proglang{R} distribution.

@@

```{r Auto}
data("Auto", package = "ISLR2")
summary(Auto)
```
With the exception of \code{origin} (which we don't use here), these variables are largely self-explanatory, except possibly for units of measurement: for details see \code{help("Auto", package="ISLR2")}.

@@

We'll focus on the relationship of \code{mpg} (miles per gallon) to \code{horsepower}, as displayed in Figure \ref{fig:mpg-horsepower-polynomials} (a). The relationship between the two variables is monotone, decreasing, and nonlinear. Following @JamesEtAl:2021, we'll consider approximating the relationship by a polynomial regression, with the degree of the polynomial $p$ ranging from 1 (a linear regression) to 10.[^log-trans] Polynomial fits  for $p = 1$ to $5$ are shown in Figure \ref{fig:mpg-horsepower-polynomials} (a). The linear fit is clearly inappropriate; the fits for $p = 2$ (quadratic) through $4$ are very similar; and the fit for $p = 5$ may over-fit the data by chasing one or two relatively high \code{mpg} values at the right (but see the CV results reported below).

[^log-trans]: Although it serves to illustrate the use of CV, a polynomial is not the best choice here. Consider, for example the scatterplot for log-transformed \code{mpg} and \code{horsepower}, produced by \code{plot(mpg ~ horsepower, data=Auto, log="xy")} (execution of which is left to the reader). We revisit the \code{Auto} data in Section \ref{cross-validating-model-specification}.

@@

The generic \code{cv()} function has an \code{"lm"} method,
```{r cv-lm-method}
args(cv:::cv.lm)
```
which takes the following arguments:

@@

```{r cv.lm-2}
cv(m.auto, k = "loo")
```
The \code{"hatvalues"} method reports only the CV estimate of MSE. Alternative methods are to use the Woodbury matrix identity or the "naive" approach of literally refitting the model with each case omitted. All three methods produce exact results for a linear model (within the precision of floating-point computations); for example:
```{r cv.lm-3}
cv(m.auto, k = "loo", method = "naive", confint = TRUE)
```
The \code{"naive"} and \code{"Woodbury"} methods also return the bias-adjusted estimate of MSE (and a confidence interval around it) along with the full-sample MSE, but bias isn't an issue for LOO CV.

@@

[^code-in-complements]: The code for this section is in the complementary materials for the paper. We used the \code{glmmTMB()} function in the \pkg{glmmTMB} package [@BrooksEtAl] for the models fit here because, in our experience, it is more likely to converge than functions in the \pkg{nlme} and the \pkg{lme4} packages for models with low between-cluster variance. We used the \pkg{lattice} [@Sarkar:2008] and \pkg{latticeExtra} [@SarkarAndrews:2022] packages for the graphs.

@@

```{r plot1, echo=FALSE, cache=TRUE}
#| out.width = "75%",
#| fig.height = 2.5,
#| fig.cap = "Data sets showing identical within-patient configurations with increasing between-patient variance. The labels above each panel show the ratio of between-patient SD to within-patient SD. The ellipses are estimated 50% Gaussian concentration ellipses for each patient. The population between-patient regression line, $\\E(y) = 10 + x$, is shown in each panel, where $y$ is symptoms and $x$ is dosage."
library("lattice")
library("latticeExtra")
layer <- latticeExtra::layer # to avert conflicts with ggplot2::layer
xyplot(y ~ x | SD_ratio, data = Data, group = patient,
       ylab = list('symptoms (y)', cex = 0.7),
       xlab = list('dosage (x)', cex = 0.7),
       par.strip.text = list(cex = 0.7),
       scales = list(cex = 0.7, x = list(alternating = FALSE)),
       layout = c(Nv, 1),
       par.settings = list(superpose.symbol = list(pch = 1, cex = 0.7))) +
  layer(panel.ellipse(..., center.pch = 16, center.cex = 0.5,  
                      level = 0.5),
        panel.abline(a = 10, b = 1))
```

Using data like these, a researcher may attempt to obtain an estimate of the within-patient effect of dosage by fitting mixed models with a random intercept. We will illustrate how this approach results in estimates that are highly sensitive to the relative variance at the two levels of the mixed model by considering four models, all of which include a random intercept.  The first three models are sequentially nested in their fixed effects: (1) \code{~ 1}, intercept only; (2) \code{~ 1 + x}, intercept and effect of \code{x}; and (3) \code{~ 1 + x + xm}, intercept, effect of \code{x}, and a contextual variable, \code{xm}, consisting of the within-patient mean of \code{x}. The final model, (4) \code{~ 1 + I(x - xm)}, uses an intercept and the centered-within-group variable \code{x - xm}. We thus fit four models to four data sets for a total of 16 models.

@@

Data sets with relatively low between-patient variance result in strong shrinkage of fixed-effects predictions, and also of BLUPs, towards the between-patient relationship between \code{y} and \code{x} in the model with an intercept and \code{x} as fixed-effect predictors, \code{~ 1 + x}. The inclusion of the contextual variable \code{xm} in the model corrects this problem.

Although the BLUPs fit the observed data more closely than predictions based on fixed effects alone, the slopes of within-patient BLUPs do not conform to the within-patient slopes for the \code{~ 1 + x} model in the two data sets with the smallest between-patient variances. For data with a small between-patient variance, fixed-effects predictions for the \code{~ 1 + x} model have a slope that is close to the between-patient slope but provide better overall predictions than the fixed-effect predictions for data sets with larger between-subject variance.  With data whose between-patient variance is relatively large, predictions based on the model with a common intercept and slope for all clusters are very poor---indeed, much worse than the fixed-effects-only predictions based on the simpler random-intercept model.

We therefore anticipate (and show later in this section) that case-based cross-validation may prefer the intercept-only model, \code{~ 1}  to the larger \code{~ 1 + x} model when the between-cluster variance is relatively small, but that cluster-based cross-validation will prefer the latter to the former. We will discover that case-based cross-validation prefers the \code{~ 1 + x} model to the \code{~ 1} model for the '5 / 2.5' data set, but cluster-based cross-validation prefers the latter model to the former. The situation is entirely reversed with the '8 / 2.5' data set.

The third model, \code{~ 1 + x + xm}, includes a contextual effect of \code{x}---that is, the cluster mean \code{xm}---along with \code{x} and the intercept in the fixed-effect part of the model, and with a random intercept. This model is equivalent to fitting \code{y ~ I(x - xm) + xm + (1 | patient)}, which is the model that generated the data.  The fit of the mixed model \code{~ 1 + x + xm} is consequently similar to that of a fixed-effects-only model with \code{x} and a categorical predictor for individual patients (i.e., \code{y ~ factor(patient) + x}, treating patients as a factor, and not shown here).

@@

[^cv-list]: In order to reduce between-model random variability in comparisons of models on the same data set, we applied \code{cv()} to a list of models created by the \code{models()} function (introduced previously), performing cross-validation with the same folds for each model.

@@

```{r cross-validation-data,include=FALSE,cache=TRUE}
names(cvs_clusters) <- names(cvs_cases) <- SD_ratio 
dsummary <- expand.grid(SD_ratio_i = names(cvs_cases), model = names(cvs_cases[[1]]))
dsummary$cases <-
  sapply(1:nrow(dsummary), function(i){
    with(dsummary[i,], cvs_cases[[SD_ratio_i]][[model]][['CV crit']])
  })
dsummary$clusters <-
  sapply(1:nrow(dsummary), function(i){
    with(dsummary[i,], cvs_clusters[[SD_ratio_i]][[model]][['CV crit']])
  })
```
```{r cross-validation-data-plot,echo=FALSE}
#| out.width = "75%",
#| fig.height = 3,
#| fig.cap = "10-fold cluster- and case-based cross-validation comparing mixed models with random intercepts and various fixed effects."
xyplot(clusters + cases ~ model|SD_ratio_i, dsummary,
       auto.key = list(space = 'top', columns = 2, cex = 0.7), 
       type = 'b', ylab = list('CV criterion (MSE)', cex = .7),
       xlab = '',
       par.strip.text = list(cex = 0.7),
       layout= c(Nv, 1),
       par.settings =
         list(superpose.line=list(lty = c(1, 2), lwd = 1),
              superpose.symbol=list(cex = 0.7)),
       scales = list(y = list(log = TRUE, cex = 0.7), 
                     x = list(alternating = F, rot = 45, cex = 0.7))) 
```
In summary, when between-cluster variance is relatively large, the model \code{~ 1 + x}, with \code{x} alone and without the contextual mean \code{xm} of \code{x}, is assessed as fitting very poorly by cluster-based CV, but relatively much better by case-based CV. In all of our examples, the model \code{~ 1 + x + xm}, which includes both \code{x} and its contextual mean, produces better results using both cluster-based and case-based CV.  These conclusions are consistent with our observations based on graphing predictions from the various models, and they illustrate the desirability of assessing mixed-effect models at different hierarchical levels.

@@

After transforming both the numeric predictors and the response, we proceed to use the \code{stepAIC()} function in the \pkg{MASS} package to perform predictor selection, employing the BIC model-selection criterion (by setting the \code{k} argument of \code{stepAIC()} to $\log n$):
```{r stepAIC}
library("MASS")
m.step <- stepAIC(m, k = log(nrow(A)), trace = FALSE)
brief(m.step)
```

@@

In Section \ref{comparing-competing-models}, following @JamesEtAl:2021[Secs. 5.1, 5.3], we fit polynomial regressions up to degree 10 to the relationship of \code{mpg} to \code{horsepower} for the \code{Auto} data, saving the 10 models, named \code{m.1} through \code{m.10}, in the list \code{mlist}. We then used \code{cv()} to compare the cross-validated MSE for the 10 models, discovering that the 7th degree polynomial had the smallest MSE (by a small margin).

If we select the 7th degree polynomial model, intending to use it for prediction, the CV estimate of the MSE for this model will be optimistic. One solution is to cross-validate the process of using CV to select the "best" model---that is, to apply CV to CV recursively. The function \code{selectModelList()}, which is suitable for use with \code{cv()}, implements this idea.

Applying \code{selectModelList()} to the \code{Auto} polynomial-regression models, and using 10-fold CV, we obtain:
```{r recursive-CV-polynomials}
recursiveCV.auto <- cv(selectModelList, data = Auto, 
                       working.model = mlist, save.model = TRUE, 
                       seed = 2120)
recursiveCV.auto
brief(recursiveCV.auto$selected.model)
cv(mlist[[7]], seed = 2120)
```
As expected, recursive CV produces a larger estimate of MSE for the selected 7th degree polynomial model than CV applied directly to this model (using the same seed for \proglang{R}'s random-number generator to obtain the same folds).

We can equivalently call \code{cv()} with the list of models as its first argument and set the argument \code{recursive = TRUE} (identical output not shown):
```{r recursive-cv-alt, eval=FALSE}
cv(mlist, data = Auto, seed = 2120, recursive = TRUE, save.model = TRUE)
```

@@

head(GetResponse(m.beps))
```
and to try again:
```{r BEPS-test-default-2, error=TRUE}
cv(m.beps, seed = 3465, criterion = BayesRuleMulti)
```
A \code{traceback()} (not shown) reveals that the problem is that the default method of \code{cv()} calls the \code{"multinom"} method for \code{predict()} with the argument \code{type="response"}, when the correct argument should be \code{type="class"}.  We therefore must write a \code{"multinom"} method for \code{cv()}, but that proves to be very simple:
```{r cv.nultinom}
cv.multinom <- function (model, data, criterion = BayesRuleMulti, 
                         k, reps, seed, ...) {
    model <- update(model, trace = FALSE)
    NextMethod(
      type = "class", criterion = criterion,
      criterion.name = deparse(substitute(criterion))
    )
  }
```
That is, we simply call the default \code{cv()} method (via \code{NextMethod()}) with the \code{type} argument properly set. In addition to supplying the correct \code{type} argument, our method sets the default \code{criterion} for the \code{cv.multinom()} method to \code{BayesRuleMulti}. Adding the argument \code{criterion.name = deparse(substitute(criterion))} is inessential, but it insures that printed output will include the name of the criterion function that's employed, whether it's the default \code{BayesRuleMulti} or something else. Prior to invoking \code{NextMethod()}, we called \code{update()} with \code{trace = FALSE} to suppress the iteration history reported by default by \code{multinom()}---it would be tedious to see the iteration history for each fold.
